Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2019-02-07 Paper.Rmd
editing completed

\begin{figure}[!h]
\begin{center}
\includegraphics[width=15 cm]{./Results/asym_sens_results/a_0.2_b_0.1_r_0.8_asym_sens.pdf}
\caption{If environmental effects operate asymmetrically in their tails on
ecological variables, it can result in non-N copula structure and asymmetric 
tail dependence across space in the ecological variables. Shown are the last
$500$ points from simulations described in the text.\label{fig_ms_asym_b_0.1}}
\end{center}
\end{figure}

>>>>

\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/asym_sens_results/a_0.2_b_0.1_r_0.8_asym_sens.pdf}
\caption{If environmental effects operate asymmetrically in their tails on
ecological variables, it can result in non-N copula structure and asymmetric 
tail dependence across space in the ecological variables. Shown are the last
$500$ points for (A) $g=g_1$ and (B) $g=g_2$ from simulations described in the text.\label{fig_ms_asym_b_0.1}}
\end{center}
\end{figure}

### 2019-02-07 SupportingInformation.Rmd
editing completed

At the same time that you do that above, please see if you can fix the alignment
between the bottom three panels of Fig S32 (and subsequent analogous figures) so they
line up with the panels above that.-->

@@

@@

tab_asym<-readRDS("./Results/asym_sens_results/stat_npa_asym_b_0.1_b_0.9.RDS")
tab_stat_npa_asym<-c()
for(i in c(1:8)){
  temp<-make_table_stat_fn(data=tab_asym[[i]])
  tab_stat_npa_asym<-rbind(tab_stat_npa_asym,temp)
}
gtext<-c("b=0.1, g$_{1}$","b=0.1, g$_{2}$","b=-0.1, g$_{1}$","b=-0.1, g$_{2}$","b=0.9, g$_{1}$","b=0.9, g$_{2}$","b=-0.9, g$_{1}$","b=-0.9, g$_{2}$")
tab_stat_npa_asym<-cbind(b=rep(c(0.1,0.1,-0.1,-0.1,0.9,0.9,-0.9,-0.9),each=3),
  g=rep(c(1,2,1,2,1,2,1,2),each=3),tab_stat_npa_asym)
knitr::kable(tab_stat_npa_asym, booktabs = T, longtable=T,
             format = "latex",linesep = "",escape=F,
             caption.short = "Asymmetric sensitivity model, nonparametric statistics results",
             caption ="Asymmetric sensitivity model, nonparametric statistics results. 
The output of simulations from the second model detailed in 
the methods section for Q2 (i.e., Figs \\ref{MT-fig_ms_asym_b_0.1} and 
\\ref{fig_ms_asym_b_-0.1}-\\ref{fig_ms_asym_b_-0.9}) were subjected to nonparamtric statistical 
analyses decribed in the methods section for Q1. The listed statistic was computed for the
output of the model with the indicated b and g, and the value was compared to 1000 values
of the same statistic computed on surrogate time series randomized to have N-copula structure
(see methods for Q1). A table entry $<X$ (respectively, $>X$) indicates the value of the 
given statistic on the data was less (respectively, more) than its value on $X$ of the 
surrogates, so entries of the form $<X$ (respectively, $>X$) for $X$ equal to $975$ or above 
indicate that upper-tail (respectively, lower-tail) dependence was significantly stronger than 
lower-tail dependence compared to an N-copula null hypothesis. `FS' stands for `first slice
and refers to the bounds 0 to 0.1; `LS' stands for `last slice' and refers to the bounds
0.9 to 1.\\label{tab_stat_npa_asym}")#%>%
 #            kable_styling()%>%
 #            group_rows(index=setNames(c(3,3,3,3,3,3,3,3), gtext))
 #            group_rows("b=0.1, g$_{1}$", 2,4, escape=F) %>%
 #            group_rows("b=0.1, g$_{2}$", 5,7, escape=F) %>%
 #            group_rows("b=-0.1, g$_{1}$", 8,10, escape=F) %>%
 #            group_rows("b=-0.1, g$_{2}$", 11,13, escape=F) %>%
 #            group_rows("b=0.9, g$_{1}$", 14,16, escape=F) %>%
 #            group_rows("b=0.9, g$_{2}$", 17,19, escape=F) %>%
 #            group_rows("b=-0.9, g$_{1}$", 20,22, escape=F) %>%
 #            group_rows("b=-0.9, g$_{2}$", 23,25, escape=F)
```

\begin{figure}[!h]
\begin{center}
\includegraphics[width=15 cm]{./Results/asym_sens_results/a_0.2_b_-0.1_r_0.8_asym_sens.pdf}
\caption{Analogous to Fig. \ref{MT-fig_ms_asym_b_0.1}, but using $b=-0.1$.\label{fig_ms_asym_b_-0.1}}
\end{center}
\end{figure}

\begin{figure}[!h]
\begin{center}
\includegraphics[width=15 cm]{./Results/asym_sens_results/a_0.2_b_0.9_r_0.8_asym_sens.pdf}
\caption{Analogous to Fig. \ref{MT-fig_ms_asym_b_0.1}, but using $b=0.9$.\label{fig_ms_asym_b_0.9}}
\end{center}
\end{figure}

\begin{figure}[!h]
\begin{center}
\includegraphics[width=15 cm]{./Results/asym_sens_results/a_0.2_b_-0.9_r_0.8_asym_sens.pdf}
\caption{Analogous to Fig. \ref{MT-fig_ms_asym_b_0.1}, but using $b=-0.9$.\label{fig_ms_asym_b_-0.9}}
\end{center}
\end{figure}

>>>>

At the same time that you do that above, please see if you can fix the alignment
between the bottom three panels of Fig S32 (and subsequent analogous figures) so they
line up with the panels above that.
***Shya: Done.-->

@@

```{r overwritting_plots_asym_cop,echo=F,results="hide"}
pdf("./Results/asym_sens_results/a_0.2_b_0.1_r_0.8_asym_sens.pdf",height=3,width=6)
op<-par(mfrow=c(1,2),mar=c(3.5,4,1,1),mgp=c(2.2,0.3,0))
pop<-ans_b_0.1$pop
plot(pop[,1],pop[,2],xlab=expression(paste(E[1])), ylab=expression(paste(E[2])),cex.lab=1.5,cex.axis=1,col="grey",pch=20,cex=0.6)
text(0.1,0.95,"A",cex=2)
pop<-ans_b_0.1$pop_d
plot(pop[,1],pop[,2],xlab=expression(paste(E[1])), ylab=expression(paste(E[2])),cex.lab=1.5,cex.axis=1,col="grey",pch=20,cex=0.6)
text(0.1,0.95,"B",cex=2)
par(op)
dev.off()

pdf("./Results/asym_sens_results/a_0.2_b_-0.1_r_0.8_asym_sens.pdf",height=3,width=6)
op<-par(mfrow=c(1,2),mar=c(3.5,4,1,1),mgp=c(2.2,0.3,0))
pop<-ans_b_neg0.1$pop
plot(pop[,1],pop[,2],xlab=expression(paste(E[1])), ylab=expression(paste(E[2])),cex.lab=1.5,cex.axis=1,col="grey",pch=20,cex=0.6)
text(0.1,0.95,"A",cex=2)
pop<-ans_b_neg0.1$pop_d
plot(pop[,1],pop[,2],xlab=expression(paste(E[1])), ylab=expression(paste(E[2])),cex.lab=1.5,cex.axis=1,col="grey",pch=20,cex=0.6)
text(0.1,0.95,"B",cex=2)
par(op)
dev.off()

pdf("./Results/asym_sens_results/a_0.2_b_0.9_r_0.8_asym_sens.pdf",height=3,width=6)
op<-par(mfrow=c(1,2),mar=c(3.5,4,1,1),mgp=c(2.2,0.3,0))
pop<-ans_b_0.9$pop
plot(pop[,1],pop[,2],xlab=expression(paste(E[1])), ylab=expression(paste(E[2])),cex.lab=1.5,cex.axis=1,col="grey",pch=20,cex=0.6)
text(0.1,0.95,"A",cex=2)
pop<-ans_b_0.9$pop_d
plot(pop[,1],pop[,2],xlab=expression(paste(E[1])), ylab=expression(paste(E[2])),cex.lab=1.5,cex.axis=1,col="grey",pch=20,cex=0.6)
text(0.1,0.95,"B",cex=2)
par(op)
dev.off()

pdf("./Results/asym_sens_results/a_0.2_b_-0.9_r_0.8_asym_sens.pdf",height=3,width=6)
op<-par(mfrow=c(1,2),mar=c(3.5,4,1,1),mgp=c(2.2,0.3,0))
pop<-ans_b_neg0.9$pop
plot(pop[,1],pop[,2],xlab=expression(paste(E[1])), ylab=expression(paste(E[2])),cex.lab=1.5,cex.axis=1,col="grey",pch=20,cex=0.6)
text(0.1,0.95,"A",cex=2)
pop<-ans_b_neg0.9$pop_d
plot(pop[,1],pop[,2],xlab=expression(paste(E[1])), ylab=expression(paste(E[2])),cex.lab=1.5,cex.axis=1,col="grey",pch=20,cex=0.6)
text(0.1,0.95,"B",cex=2)
par(op)
dev.off()
```

@@

tab_asym<-readRDS("./Results/asym_sens_results/stat_npa_asym_b_0.1_b_0.9.RDS")
tab_stat_npa_asym<-c()
for(i in c(1:8)){
  temp<-make_table_stat_fn(data=tab_asym[[i]])
  tab_stat_npa_asym<-rbind(tab_stat_npa_asym,temp)
}
gtext<-c("b=0.1, g$_{1}$","b=0.1, g$_{2}$","b=-0.1, g$_{1}$","b=-0.1, g$_{2}$","b=0.9, g$_{1}$","b=0.9, g$_{2}$","b=-0.9, g$_{1}$","b=-0.9, g$_{2}$")
tab_stat_npa_asym<-cbind(b=rep(c(0.1,0.1,-0.1,-0.1,0.9,0.9,-0.9,-0.9),each=3),
  g=rep(c("g$_{1}$","g$_{2}$","g$_{1}$","g$_{2}$","g$_{1}$","g$_{2}$","g$_{1}$","g$_{2}$"),each=3),tab_stat_npa_asym)
knitr::kable(tab_stat_npa_asym, booktabs = T, longtable=T,
             format = "latex",linesep = "",escape=F,
             caption.short = "Asymmetric sensitivity model, nonparametric statistics results",
             caption ="Asymmetric sensitivity model, nonparametric statistics results. 
The output of simulations from the second model detailed in 
the methods section for Q2 (i.e., Figs \\ref{MT-fig_ms_asym_b_0.1} and 
\\ref{fig_ms_asym_b_-0.1}-\\ref{fig_ms_asym_b_-0.9}) were subjected to nonparamtric statistical 
analyses decribed in the methods section for Q1. The listed statistic was computed for the
output of the model with the indicated b and g, and the value was compared to 1000 values
of the same statistic computed on surrogate time series randomized to have N-copula structure
(see methods for Q1). A table entry $<X$ (respectively, $>X$) indicates the value of the 
given statistic on the data was less (respectively, more) than its value on $X$ of the 
surrogates, so entries of the form $<X$ (respectively, $>X$) for $X$ equal to $975$ or above 
indicate that upper-tail (respectively, lower-tail) dependence was significantly stronger than 
lower-tail dependence compared to an N-copula null hypothesis. `FS' stands for `first slice'
and refers to the bounds 0 to 0.1; `LS' stands for `last slice' and refers to the bounds
0.9 to 1.\\label{tab_stat_npa_asym}")#%>%
 #            kable_styling()%>%
 #            group_rows(index=setNames(c(3,3,3,3,3,3,3,3), gtext))
 #            group_rows("b=0.1, g$_{1}$", 2,4, escape=F) %>%
 #            group_rows("b=0.1, g$_{2}$", 5,7, escape=F) %>%
 #            group_rows("b=-0.1, g$_{1}$", 8,10, escape=F) %>%
 #            group_rows("b=-0.1, g$_{2}$", 11,13, escape=F) %>%
 #            group_rows("b=0.9, g$_{1}$", 14,16, escape=F) %>%
 #            group_rows("b=0.9, g$_{2}$", 17,19, escape=F) %>%
 #            group_rows("b=-0.9, g$_{1}$", 20,22, escape=F) %>%
 #            group_rows("b=-0.9, g$_{2}$", 23,25, escape=F)
```

\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/asym_sens_results/a_0.2_b_-0.1_r_0.8_asym_sens.pdf}
\caption{Analogous to Fig. \ref{MT-fig_ms_asym_b_0.1}, but using $b=-0.1$.\label{fig_ms_asym_b_-0.1}}
\end{center}
\end{figure}

\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/asym_sens_results/a_0.2_b_0.9_r_0.8_asym_sens.pdf}
\caption{Analogous to Fig. \ref{MT-fig_ms_asym_b_0.1}, but using $b=0.9$.\label{fig_ms_asym_b_0.9}}
\end{center}
\end{figure}

\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/asym_sens_results/a_0.2_b_-0.9_r_0.8_asym_sens.pdf}
\caption{Analogous to Fig. \ref{MT-fig_ms_asym_b_0.1}, but using $b=-0.9$.\label{fig_ms_asym_b_-0.9}}
\end{center}
\end{figure}
